---
title: "Covid 19"
author: "Amee Rodrick"
date: "10/21/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 
### This is contained in a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Question 1 - Is dying independent of sex




Table of patients:
```{r}

# cross tabulation, patient state by gender

with(kRdata, table(Sex, result))

```

## We create two bar charts - one based on frequency and the other on percent

```{r}
barchartGC(~result + Sex,data=kRdata, main ="Frequency Bar Chart")

```

  
### this bar chart is displaying in total frequency terms our data.  Clearly there are a lot less dead people than alive people as is reflected by the sizes of the bars in the display.  
```{r}
barchartGC(~result + Sex,data=kRdata, type= "percent")
```



As we can see in the above bar chart the people alive, roughly 55% are female and 43% of men. Males are dying from Covid. 


  
## Numerical results

```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```

Im the above results 64% of men are dead and 36% of female have died from Covid. 

## Inferential results 

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

Looking at the numbers above more men have died unexpectedly and less women died then expected.Meaning men are more vulnerable to the disease Covid. P value is 9e=04 which is a very small number.


## Conclusions
My conclusion based on data is that men infected with Covid are dying at a higher rate the the infected women. 










